Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
update

\begin{lstlisting}[style=default]
(sample :arrival-time-same
        time-to-arrive-prior)]

(sample :arrival-time-first
        time-to-arrive-prior)

(sample :arrival-time-second
        time-to-arrive-prior)]

(let [is-same-customer (sample :same-or-different
                               (flip p-same))
\end{lstlisting}

>>>>

\begin{lstlisting}[style=default]
(defm same-customer 
      ...
      (sample :arrival-time-same
              time-to-arrive-prior)]
      ...)

(defm different-customers
      ... 
      (sample :arrival-time-first
              time-to-arrive-prior)
      ...
      (sample :arrival-time-second
              time-to-arrive-prior)]
      ...)

(defquery deli ...
      ...
      (sample :same-or-different
              (flip p-same))
      ...)
\end{lstlisting}
